---
title: "ZWillensHW5"
author: "Zach Willens, and Skyler Young"
date: "2023-03-06"
output: html_document
---


```{r}
choco <- read.csv("https://ds202-at-isu.github.io/labs/data/choco.csv")
head(choco)
```

What is the overall number of chocolate bars rated?
Answer: 1852
```{r}
num_reports = nrow(choco)
num_reports
```

How does the number of ratings depend on the year? Draw a bar chart of the number of reports.
Typically, as time passes, the quantity of ratings tends to rise, indicating a positive correlation between the year and the ratings.

```{r}
library(ggplot2)
bar_chart = ggplot(data=choco, aes(x=Review.Date, y=num_reports)) +
  geom_bar(stat="identity", width=.75, fill="blue")+theme_minimal()
bar_chart
```
How are ratings distributed? Draw a histogram of ratings and describe it. Don’t forget to mention outliers, if there are any.

The average and median ratings are both at 3, with a distribution that leans slightly towards the left but can also be considered symmetrical. However, there is one outlier at a rating of 5.
```{r}
mpg_hist = ggplot(choco, aes(x=Rating)) + 
  geom_histogram(binwidth=1)

mpg_hist
```
Do ratings depend on the cocoa percentage of a chocolate bar?
There is a lack of correlation between the cocoa percentage and the rating of the chocolate bars.

```{r}
mpg_scatter = ggplot(choco, aes(x = Cocoa.Pct, y = Rating)) +
    geom_point()
mpg_scatter + geom_jitter()
```


How do ratings compare across different company locations? Focus on the three locations with the most ratings:

The three countries with the highest number of ratings have a similar median rating of approximately 3.2. However, there are notable differences in the distribution of ratings among these countries. Canada and the US both exhibit a left skewness and have greater variability in their ratings compared to France, which has a symmetrical distribution and lower variability. Moreover, the US has two outliers, while France and Canada have one outlier and no outliers, respectively.

```{r}
var = dplyr::filter(choco, Company.Location %in% c("U.S.A.", "France", "Canada"))
# boxplots
ggplot(var, aes(x = Rating, y = Company.Location )) +
  geom_boxplot()+
  labs(
    title = "Chocolate rating for 3 countries",
    x = "Rating",
    y = "Country"
  ) +
  theme_classic()
```

